---
title: "testkeras -- do keras 3 and python 3.12 work with basilisk?"
shorttitle: "testing basilisk and session_info in python/reticulate"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{testkeras -- do keras 3 and python 3.12 work with basilisk?}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

```{r setup,message=FALSE}
library(testkeras)
```

# Introduction

This package defines two functions.

- lksk shows that one can obtain the "version signature" of
a collection of python packages, using a basilisk environment.

The environment is
```{r lkenv}
testkeras:::bsklenv
```

lksk is
```{r lklk1}
lksk
```

- lkker demonstrates that we can use keras3 through basilisk.
But it cannot obtain the signature of versions of python modules
because of a problem using `pybind11_abseil`.

```{r lklk2}
lkker
```

# Modules needed with scikit-learn

```{r lklk3}
lksk()
```

# Using keras

```{r lklk4}
kk = lkker()
names(kk) # good
# not working as expected:
reticulate::py_capture_output(reticulate::py_help(kk$keras))
```

# Session Info

```{r lksess}
sessionInfo()
```
